\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-29 to-do2.tex
add language for letter to editor on sequential model

	\item[26.] The full separability of sectors implies very minimal interactions already. Assuming a fully symmetric model is then highly restrictive. How difficult would it be to relax the latter assumption?

>>>>

			\item As long as there is a move of nature that occurs \textit{after} the trade agreement tariffs are set that determines which country's legislature moves first, at a first pass the results seem to go through with little additional complication for the sequential model you suggest.

			The current results would apply for the second mover and a new set of results would need to be added for the actors in the country that is the first mover since their objective functions are altered by the future chance that the second moving legislature will break the agreement if the first moving legislature does not. This adds a nice new result that was only mentioned in passing in the previous draft about the first-mover lobby free-riding on the potential effort of the second-mover lobby. This is also why preserving the current results would require that the executives are behind a veil of ignorance about which country's legislature moves first: if they knew, they would like to exploit this information to reduce the tariff in the country where the lobby will suffer from the free-riding incentive. While there are probably some countries in which an executive can control the timing of a vote, it's probably fairly realistic to think that executives do know know for sure in which of their countries a vote will first take place. I can handle the case of asymmetric tariffs, but some of the propositions rely on the symmetry in tariffs for simplicity and I believe an extra condition would have to be invoked in several cases to bound magnitudes. I would like to avoid this especially if complicating the model further.

			I think that this modification of the model adds something beneficial, but the tradeoff is both in terms of complexity and, necessarily, length. Thus I write to ask your opinion given your request to cut the length of the paper in half. I am working toward this end, but I do not see that this is possible if I were to add this complication and new results that go along with it.

		\end{itemize}
	\item[26.] The full separability of sectors implies very minimal interactions already. Assuming a fully symmetric model is then highly restrictive. How difficult would it be to relax the latter assumption?
\end{enumerate}
